Additional analysis

### 2019-02-26 03_additional-analysis.Rmd
95% everywhere + tibble()

  tidied <- tidyMCMC(mcmc_samples, conf.int = TRUE, conf.level = 0.9, 
                     estimate.method = "median", conf.method = "HPDinterval") %>%
    mutate(in_hpdi = (population_value >= conf.low & population_value <= conf.high))

@@

tbl_sample_pop <- calc_sample_pop %>% 
  mutate(in_hpdi = prop_test_bayes %>% map_lgl(~ .$theta_in_hpdi),
         not_hpdi_symbol = ifelse(in_hpdi, "", "^†^"),
         diffs_tidy = prop_test_bayes %>% map(~ .$tidied[2,]),
         diffs_median = diffs_tidy %>% map_dbl(~ .$estimate),
         diffs_hpdi_fancy = diffs_tidy %>%
           map2_chr(.x = diffs_tidy, .y = not_hpdi_symbol, 
                    .f = ~ format_hpdi(.x$conf.low, .x$conf.high, .y))) %>% 
  mutate_at(vars(National, Sample, diffs_median), funs(percent)) %>% 
  select(Variable, Sample, National, 
         `∆~median~` = diffs_median,
         `90% HPDI` = diffs_hpdi_fancy)

note_row <- data_frame(Variable = c("*^a^Annual CPS, March 2017*",
                                    "*^b^Monthly CPS, September 2015*",
                                    "*^†^National value is outside the sample highest posterior density interval (HPDI)*"))

@@

```{r models-coefs-plot-amount, warning=FALSE, message=FALSE, fig.width=8, fig.height=5}
posterior_details <- data_frame(model_name = c("Basic model", "Full model"),
                                model = list(m_amount_cif,
                                             m_amount_cif_full)) %>% 
  mutate(posterior = model %>% map(~ as_data_frame(.)),
         tidy_summary = model %>% map(~ tidyMCMC(., conf.int = TRUE, conf.level = 0.9,
                                                 conf.method = "HPDinterval")))

@@

amount_coefs_full <- ggplot(coefs_posterior, aes(x = value, y = fct_rev(term_clean_fct))) +
  stat_density_ridges(aes(fill = model_name), alpha = 0.6, color = "black",
                      rel_min_height = 0.01, scale = 1.5, 
                      quantile_lines = TRUE, quantiles = 2) +
  geom_segment(data = coefs_summary, 
               aes(x = conf.low, xend = conf.high, 
                   y = fct_rev(term_clean_fct), yend = fct_rev(term_clean_fct)),
               size = 1) +
  geom_vline(xintercept = 0, linetype = "dotted", size = 1) + 
  scale_fill_manual(values = ngo_cols("red", "blue", name = FALSE), name = NULL) +
  labs(x = "Posterior median estimate + 90% credible interval", y = NULL,
       caption = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0") +
  facet_wrap(~ full_model, scales = "free") + 
  theme_ngos() +
  theme(legend.position = "bottom",
        strip.text = element_blank())

@@

coef_summary_charity <- newdata_conditions_charity %>% 
  bind_cols(tidyMCMC(chains_fitted_charity, estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval")) %>% 
  mutate_at(vars(crackdown, give_charity_3), funs(fct_inorder(., ordered = TRUE)))

@@

coef_summary_vol_relig <- newdata_conditions_vol_relig %>% 
  bind_cols(tidyMCMC(chains_fitted_vol_relig, estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval")) %>% 
  mutate_at(vars(crackdown, volunteer, religiosity_bin), funs(fct_inorder(., ordered = TRUE))) %>% 
  mutate(religiosity_bin = fct_recode(religiosity_bin,
                                      `Rarely attend religious services` = "Rarely",
                                      `Attend religious services\nat least once a month` = 
                                        "At least once a month"))

@@

```{r models-coefs-plot-likely, warning=FALSE, message=FALSE, fig.width=8, fig.height=5}
posterior_details_likely <- data_frame(model_name = c("Basic model", "Full model"),
                                       model = list(m_likely_cif,
                                                    m_likely_cif_full)) %>% 
  mutate(posterior = model %>% map(~ as_data_frame(.)),
         tidy_summary = model %>% map(~ tidyMCMC(., conf.int = TRUE, conf.level = 0.9,
                                                 conf.method = "HPDinterval")))

@@

likely_coefs_full <- ggplot(coefs_posterior_likely, aes(x = value, y = fct_rev(term_clean_fct))) +
  stat_density_ridges(aes(fill = model_name), alpha = 0.6, color = "black",
                      rel_min_height = 0.01, scale = 1.5, 
                      quantile_lines = TRUE, quantiles = 2) +
  geom_segment(data = coefs_summary_likely, 
               aes(x = conf.low, xend = conf.high, 
                   y = fct_rev(term_clean_fct), yend = fct_rev(term_clean_fct)),
               size = 1) +
  geom_vline(xintercept = 0, linetype = "dotted", size = 1) + 
  scale_fill_manual(values = ngo_cols("red", "blue", name = FALSE), name = NULL) +
  labs(x = "Posterior median estimate + 90% credible interval", y = NULL,
       caption = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0") +
  facet_wrap(~ full_model, scales = "free") + 
  theme_ngos() +
  theme(legend.position = "bottom",
        strip.text = element_blank())

>>>>

  tidied <- tidyMCMC(mcmc_samples, conf.int = TRUE, conf.level = 0.95, 
                     estimate.method = "median", conf.method = "HPDinterval") %>%
    mutate(in_hpdi = (population_value >= conf.low & population_value <= conf.high))

@@

tbl_sample_pop <- calc_sample_pop %>% 
  mutate(in_hpdi = prop_test_bayes %>% map_lgl(~ .$theta_in_hpdi),
         not_hpdi_symbol = ifelse(in_hpdi, "", "^†^"),
         diffs_tidy = prop_test_bayes %>% map(~ .$tidied[2,]),
         diffs_median = diffs_tidy %>% map_dbl(~ .$estimate),
         diffs_hpdi_fancy = diffs_tidy %>%
           map2_chr(.x = diffs_tidy, .y = not_hpdi_symbol, 
                    .f = ~ format_hpdi(.x$conf.low, .x$conf.high, .y))) %>% 
  mutate_at(vars(National, Sample, diffs_median), funs(percent)) %>% 
  select(Variable, Sample, National, 
         `∆~median~` = diffs_median,
         `95% HPDI` = diffs_hpdi_fancy)

note_row <- tibble(Variable = c("*^a^Annual CPS, March 2017*",
                                "*^b^Monthly CPS, September 2015*",
                                "*^†^National value is outside the sample highest posterior density interval (HPDI)*"))

@@

```{r models-coefs-plot-amount, warning=FALSE, message=FALSE, fig.width=8, fig.height=5}
posterior_details <- tibble(model_name = c("Basic model", "Full model"),
                            model = list(m_amount_cif,
                                         m_amount_cif_full)) %>% 
  mutate(posterior = model %>% map(~ as_tibble(.)),
         tidy_summary = model %>% map(~ tidyMCMC(., conf.int = TRUE, conf.level = 0.95,
                                                 conf.method = "HPDinterval")))

@@

amount_coefs_full <- ggplot(coefs_posterior, aes(x = value, y = fct_rev(term_clean_fct))) +
  stat_density_ridges(aes(fill = model_name), alpha = 0.6, color = "black",
                      rel_min_height = 0.01, scale = 1.5, 
                      quantile_lines = TRUE, quantiles = 2) +
  geom_segment(data = coefs_summary, 
               aes(x = conf.low, xend = conf.high, 
                   y = fct_rev(term_clean_fct), yend = fct_rev(term_clean_fct)),
               size = 1) +
  geom_vline(xintercept = 0, linetype = "dotted", size = 1) + 
  scale_fill_manual(values = ngo_cols("red", "blue", name = FALSE), name = NULL) +
  labs(x = "Posterior median estimate + 95% credible interval", y = NULL,
       caption = "95% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0") +
  facet_wrap(~ full_model, scales = "free") + 
  theme_ngos() +
  theme(legend.position = "bottom",
        strip.text = element_blank())

@@

coef_summary_charity <- newdata_conditions_charity %>% 
  bind_cols(tidyMCMC(chains_fitted_charity, estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.95, conf.method = "HPDinterval")) %>% 
  mutate_at(vars(crackdown, give_charity_3), funs(fct_inorder(., ordered = TRUE)))

@@

coef_summary_vol_relig <- newdata_conditions_vol_relig %>% 
  bind_cols(tidyMCMC(chains_fitted_vol_relig, estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.95, conf.method = "HPDinterval")) %>% 
  mutate_at(vars(crackdown, volunteer, religiosity_bin), funs(fct_inorder(., ordered = TRUE))) %>% 
  mutate(religiosity_bin = fct_recode(religiosity_bin,
                                      `Rarely attend religious services` = "Rarely",
                                      `Attend religious services\nat least once a month` = 
                                        "At least once a month"))

@@

```{r models-coefs-plot-likely, warning=FALSE, message=FALSE, fig.width=8, fig.height=5}
posterior_details_likely <- tibble(model_name = c("Basic model", "Full model"),
                                   model = list(m_likely_cif,
                                                m_likely_cif_full)) %>% 
  mutate(posterior = model %>% map(~ as_tibble(.)),
         tidy_summary = model %>% map(~ tidyMCMC(., conf.int = TRUE, conf.level = 0.95,
                                                 conf.method = "HPDinterval")))

@@

likely_coefs_full <- ggplot(coefs_posterior_likely, aes(x = value, y = fct_rev(term_clean_fct))) +
  stat_density_ridges(aes(fill = model_name), alpha = 0.6, color = "black",
                      rel_min_height = 0.01, scale = 1.5, 
                      quantile_lines = TRUE, quantiles = 2) +
  geom_segment(data = coefs_summary_likely, 
               aes(x = conf.low, xend = conf.high, 
                   y = fct_rev(term_clean_fct), yend = fct_rev(term_clean_fct)),
               size = 1) +
  geom_vline(xintercept = 0, linetype = "dotted", size = 1) + 
  scale_fill_manual(values = ngo_cols("red", "blue", name = FALSE), name = NULL) +
  labs(x = "Posterior median estimate + 95% credible interval", y = NULL,
       caption = "95% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0") +
  facet_wrap(~ full_model, scales = "free") + 
  theme_ngos() +
  theme(legend.position = "bottom",
        strip.text = element_blank())
